Understanding Factors Contributing to Application Approval in Urban Planning Decisions (2016-2024)

### 2024-12-04 paper/paper.qmd
Paper Revision

`Sampling: Design and Analysis` (@lohr2021sampling) explores how stratified sampling reduces variability by dividing populations into homogeneous groups, enabling more precise estimates and better resource allocation. By applying these principles, the paper ensures that the analysis accounts for heterogeneity in geographic and temporal patterns of planning applications, enabling robust conclusions about decision-making trends. The methodology follows Lohr’s recommendation to tailor strata definitions to the study's objectives, enhancing the reliability of the results.

Besides, `Sampling` (@thompson2012sampling) provides a detailed guide to modern sampling techniques, emphasizing the importance of tailoring approaches to study objectives. His discussion on stratified sampling highlights its benefits in improving precision and reducing bias by dividing populations into homogeneous subgroups. This aligns with the choice of using planning districts, application types, and submission years as strata to ensure balanced representation and capture temporal and spatial variability in urban planning decisions. Thompson’s principles validate the proportional sampling approach adopted here, supporting its effectiveness in generating reliable analyses.

>>>>

`Sampling: Design and Analysis` [@lohr2021sampling] explores how stratified sampling reduces variability by dividing populations into homogeneous groups, enabling more precise estimates and better resource allocation. By applying these principles, the paper ensures that the analysis accounts for heterogeneity in geographic and temporal patterns of planning applications, enabling robust conclusions about decision-making trends. The methodology follows Lohr’s recommendation to tailor strata definitions to the study's objectives, enhancing the reliability of the results.

Besides, `Sampling` [@thompson2012sampling] provides a detailed guide to modern sampling techniques, emphasizing the importance of tailoring approaches to study objectives. His discussion on stratified sampling highlights its benefits in improving precision and reducing bias by dividing populations into homogeneous subgroups. This aligns with the choice of using planning districts, application types, and submission years as strata to ensure balanced representation and capture temporal and spatial variability in urban planning decisions. Thompson’s principles validate the proportional sampling approach adopted here, supporting its effectiveness in generating reliable analyses.
